Total Score

### 2023-02-14 src/MSAtotal_scores.Rmd
output real estate metrics to google sheet

tiff(filename = "wt_criteria_client_chart.tiff", width = 8, height = 6, units = "in", res = 300)
ggplot(data = score_tidy, aes(y = reorder(msa_state, FINAL_owen_SCORE), x = criteria_score)) +
    geom_col(aes(fill = criteria)) +
  labs(x = "Total Score",
       y = " ",
       title = "Client") +
  theme_bw() +
  guides(fill=guide_legend(title="Criteria (weighted)")) +
   scale_fill_manual(values = c("palevioletred1","#FDB462",  "gold", "#44AA99", "dodgerblue4", "#BC80BD"),
                     labels=c('Climate Risk', 'CO2 Emissions', 'Electricity', "Solar IRR", "Real Estate", "Landlord Policy")) +
  scale_x_continuous(limits = c(0, 0.7), expand = c(0,0), breaks=seq(0, 0.7, 0.1))
dev.off()
```

@@

tiff(filename = "wt_criteria_student_chart.tiff", width = 8, height = 6, units = "in", res = 300)
ggplot(data = score_tidy2, aes(y = reorder(msa_state, FINAL_st_score), x = criteria_score)) + 
    geom_col(aes(fill = criteria)) +
  labs(x = "Total Score",
       y = " ",
       title = "Student") +
  theme_bw() +
  guides(fill=guide_legend(title="Criteria (weighted)")) +
   scale_fill_manual(values = c("palevioletred1","#FDB462",  "gold", "#44AA99", "dodgerblue4", "#BC80BD"),
                     labels=c('Climate Risk', 'CO2 Emissions', 'Electricity', "Solar IRR", "Real Estate", "Health Impacts")) +
  scale_x_continuous(limits = c(0, 0.8), expand = c(0,0), breaks=seq(0, 0.8, 0.1))
dev.off()
```

>>>>

tiff(filename = "wt_criteria_client_chart.tiff",width = 8, height = 6, units = "in", res = 300, pointsize = 12)
ggplot(data = score_tidy, aes(y = reorder(msa_state, FINAL_owen_SCORE), x = criteria_score)) +
    geom_col(aes(fill = criteria)) +
  labs(x = "Total Score",
       y = " ",
       title = "Client") +
  theme_bw() +
  guides(fill=guide_legend(title="Criteria (weighted)")) +
   scale_fill_manual(values = c("palevioletred1","orange",  "gold", "#44AA99", "dodgerblue4", "#BC80BD"),
                     labels=c('Climate Risk', 'CO2 Emissions', 'Electricity', "Solar IRR", "Real Estate", "Landlord Policy")) +
  scale_x_continuous(limits = c(0, 0.7), expand = c(0,0), breaks=seq(0, 0.7, 0.1))
dev.off()
```

@@

tiff(filename = "wt_criteria_student_chart.tiff", width = 8, height = 6, units = "in", res = 300)
ggplot(data = score_tidy2, aes(y = reorder(msa_state, FINAL_st_score), x = criteria_score)) + 
    geom_col(aes(fill = criteria)) +
  labs(x = "Total Score",
       y = " ",
       title = "Student") +
  theme_bw() +
  guides(fill=guide_legend(title="Criteria (weighted)")) +
   scale_fill_manual(values = c("palevioletred1", "orange",  "gold", "#44AA99", "dodgerblue4", "#6495ED"),
                     labels=c('Climate Risk', 'CO2 Emissions', 'Electricity', "Solar IRR", "Real Estate", "Health Impacts")) +
  scale_x_continuous(limits = c(0, 0.8), expand = c(0,0), breaks=seq(0, 0.8, 0.1))
dev.off()
```
